---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ChatGPT coding assistant for RStudio

<center>
    <img width="300" height="400" src="https://media.licdn.com/dms/image/C5622AQG8D9NQ_ePuzA/feedshare-shrink_800/0/1673359083125?e=1676505600&v=beta&t=cnmYmdjyiAZ4gwZqqwJy1UXBJ5IlHWAiLWLQuSEjeYk">
    <p>Meme by Programming Jokes I IT Humor & Memes</p>
</center>

## Installation

You can install the development version of {chatgpt} from [GitHub](https://github.com/jcrodriguez1989/chatgpt) with:

``` r
# install.packages("remotes")
remotes::install_github("jcrodriguez1989/chatgpt")
```

## Requirements

You need to setup your ChatGPT API key in R.

First you will need to obtain your ChatGPT API key. You can create an API key by accessing [OpenAI API page](https://beta.openai.com/account/api-keys) -don't miss their article about [Best Practices for API Key Safety
](https://help.openai.com/en/articles/5112595-best-practices-for-api-key-safety)-.

Then you have to assign your API key for usage in R, this can be done just for the actual session, by doing:

``` r
Sys.setenv(OPENAI_API_KEY = "XX-XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX")
```

Or you can do it persistent (session-wide), by assigning it in your `.Renviron` file. For it, execute `usethis::edit_r_environ()`, and in that file write a line at the end your API key as

``` r
OPENAI_API_KEY=XX-XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
```.

## Features

The {chatgpt} R package provides a set of features to assist in R coding. 
Current existing addins:

```{r, echo=FALSE, results='asis'}
addins_info <- readLines("inst/rstudio/addins.dcf")
addins_info <- addins_info[grepl("^(Name: |Description: )", addins_info)]
addins_info <- gsub("^(Name: |Description: )", "", addins_info)
indexes <- seq_len(length(addins_info))
indexes <- indexes[indexes %% 2 == 1]
cat(paste(
  sapply(indexes, function(i) paste0(" - **", addins_info[[i]], ":** ", addins_info[[i + 1]])),
  collapse = "\n"
))
```

**Note:** When no code is selected, it will use the whole file's code.
